Leadership across cultures and contexts: an exploratory analysis

### 2020-05-03 leadership_across_cultures_contexts.Rmd

Our third goal was to determine which leader and follower benefits and costs were most commonly mentioned in the ethnographic record, computing proportions and 95% CIs as above and to estimate how costs and benefits varied by group structure types and other population-level measures.

To supplement results from the aforementioned methods, we also performed textual analyses and explored variation in measures of biases stemming from the ethnographic record that may have impacted results.

>>>>

To supplement results from the aforementioned methods, we also performed textual analyses and explored variation measures of biases stemming from the ethnographic record that may have impacted results.
